Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-05-10 paper/paper.tex
fix(paper): Use \path for long paths

All contents, including source files and resulting build artifacts, are stored inside the Nix store.
Per default, the Nix store resides in the path \texttt{/nix/store} on the file system.
The naming scheme for the preCICE 2.5.0 package as an example is \texttt{/nix/store/0a5gw3l\ldots-precice-2.5.0}.
This eases checking the Nix store for integrity and ensures that builds using the same inputs are performed only once.

@@

Another dependency, that is also provided by code\_aster is metis, that partially builds, so we do not replace this dependency, but we need to fix the second part of the build, including the metis programs such as gpmetis, ndmetis, mpmetis and more.
The issue is that in the \texttt{CMakeLists.txt} for the metis programs \texttt{link\_directories} is hard-coded to \texttt{/home/karypis/local/lib}.
After removing this line, it also installs, so to resolve this issue in the buildPhase, we unpack the metis tarball, remove this line with \texttt{sed} and then repack the directory.

@@

The issue is that the custom build system does not correctly calculate the python site-packages directory because it unconditionally slices the first 3 chars from \texttt{sys.version}, that works if your version is 3.9.x but not with 3.10.x because then the code calculates \texttt{lib64/python3.1/site-packages} rather than the expected \texttt{lib64/python3.10/site-packages}.

>>>>

All contents, including source files and resulting build artifacts, are stored inside the Nix store.
Per default, the Nix store resides in the path \texttt{/nix/store} on the file system.
The naming scheme for the preCICE 2.5.0 package as an example is \path{/nix/store/0a5gw3l\ldots-precice-2.5.0}.
This eases checking the Nix store for integrity and ensures that builds using the same inputs are performed only once.

@@

Another dependency, that is also provided by code\_aster is metis, that partially builds, so we do not replace this dependency, but we need to fix the second part of the build, including the metis programs such as gpmetis, ndmetis, mpmetis and more.
The issue is that in the \texttt{CMakeLists.txt} for the metis programs \texttt{link\_directories} is hard-coded to \path{/home/karypis/local/lib}.
After removing this line, it also installs, so to resolve this issue in the buildPhase, we unpack the metis tarball, remove this line with \texttt{sed} and then repack the directory.

@@

The issue is that the custom build system does not correctly calculate the python site-packages directory because it unconditionally slices the first 3 chars from \texttt{sys.version}, that works if your version is 3.9.x but not with 3.10.x because then the code calculates \path{lib64/python3.1/site-packages} rather than the expected \path{lib64/python3.10/site-packages}.
